---
title: "Song_popularity"
author: "Yi"
date: "10/21/2022"
output: pdf_document
---

```{r echo=FALSE}
library(tidyverse)
library(ggplot2)

r <- read.csv("song_data.csv")

# Store a copy of data
rr <- r %>%
  filter(tempo > 0, tempo < 225, loudness < 0) %>%
  select(song_popularity, danceability, acousticness, energy, loudness, audio_valence, tempo)

```



```{r include=FALSE, eval=FALSE}

# Scatter plots of the predictor vs. response
p1 <- ggplot(rr, aes(x = danceability, y = song_popularity)) +
    geom_point() + 
  labs(
      x = "Danceability",
      y = "Song Popularity"
    )

p2 <- ggplot(rr, aes(acousticness, song_popularity)) +
  geom_point()+ 
  labs(
      x = "Acousticness",
      y = "Song Popularity"
    )

p3 <- ggplot(rr, aes(tempo, song_popularity)) +
  geom_point() + 
  labs(
      x = "Tempo",
      y = "Song Popularity"
    )

p4 <- ggplot(rr, aes(audio_valence, song_popularity)) +
  geom_point() + 
  labs(
      x = "Audio Valence",
      y = "Song Popularity"
    )

p5 <- ggplot(rr, aes(loudness, song_popularity)) +
  geom_point() + 
  labs(
      x = "Loudness",
      y = "Song Popularity"
    )

p6 <- ggplot(rr, aes(energy, song_popularity)) +
  geom_point() + 
  labs(
      x = "Energy",
      y = "Song Popularity"
    )

p1
p2
p3
p4
p5
p6
```


```{r include=FALSE, echo=FALSE}

# Histograms of the predictors vs. response

h1 <- ggplot(r, aes(x = song_popularity)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Song Popularity", y = "Counts")

h2 <- ggplot(r, aes(x = danceability)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Danceability", y = "Counts")

h3 <- ggplot(r, aes(x = acousticness)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Acousticness", y = "Counts")

h4 <- ggplot(r, aes(x = tempo)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Tempo", y = "Counts")

h5 <- ggplot(r, aes(x = audio_valence)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Audio Valence", y = "Counts")

h6 <- ggplot(r, aes(x = loudness)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Loudness", y = "Counts")

h7 <- ggplot(r, aes(x = energy)) +
  geom_histogram(colour = 4, fill = "white", bins = 25) +
  labs(x = "Energy", y = "Counts")

h1
h2
h3
h4
h5
h6
h7

```


```{r include=FALSE, echo=FALSE}

r1 <- r %>%
  filter(tempo > 0, tempo < 225, loudness < 0) %>%
  select(song_popularity, danceability, acousticness, energy, loudness, audio_valence, tempo) %>%
  summary()
```




Characteristics of variables

| variable name | min | median | max | mean |
|---------------|------|--------|----------|
| `song_popularity`|0.00|56.00|100.00|53.00|
| `danceability`|0.0594|0.6450|0.9870|0.6334|
|`acousticness`|0.000001|0.133000|0.996000|0.258616|
|`energy`|0.00107|0.67400|0.999900|0.64490|
|`loudness`|-38.768|-6.557|-0.257|-7.450|
|`audio_valence`|0.023|0.527|0.984|0.528|
|`tempo`|46.59|120.01|216.12|121.07|



Data Description

| variable name |Description|
|---------------|----------|
|`danceability`|How suitable the track is for dancing with the range from 0.0 to 1.0|
|`acousticness`|To tell if the track is acoustic or not with the confidence measure from 0.0 to 1.0|
|`tempo`|The estimated pace of the track|
|`audio_valence`|The musical positivity of the track with the range from 0.0 to 1.0|
|`energy`|The intensity and activity of the track with the range from 0.0 to 1.0|
|`loudness`|The measure of loudness of the track with the range from -60.0 to 0.0|
|`song_popularity`|How popular the song is with the range from 0.0 to 100.0|


Appendix

```{r echo=FALSE}
glimpse(rr)
```







